Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-31 PAPER.tex
re-compiled updated plots

In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{out} = \widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$. Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?". \acl{Can we justify better why this is the right question? In particular, why is the detection of an injected signal the right thing to look at? After all, the universe doesn't do any signal injections. I think to justify that signal injections are the right thing to consider in the first place, one requires some sort of correspondence between equations analogous to Equation \eqref{eq:Deriv1} and \eqref{eq:Deriv2}.} Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
\caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
given injection level P$_{in}$. The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal. It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}). We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution. At low injection, $\widehat{\textbf{p}}_{r}$ converges to the data level.
}
\label{fig:Pr_vs_Pin}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
\caption{The probability that an injected signal of level P$_{inj}$
is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{p}}_{x}$ (data).
The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.
\label{fig:Prob_vs_Pin}}
\end{figure}

@@

Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of "data + 
injected eor" ($\widehat{p}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{p}_x$. 
In other words, what is $e$ such that,
\begin{equation}
\widehat{\textbf{p}}_{e+x} > \widehat{\textbf{p}}_{x},
\end{equation}  
?''  Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance. One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e. the null test) the same.  
 \acl{I'm confused a little by this equation. I would've thought that the right thing to do would be to first compute $x_0$, given implicitly by
 \begin{equation}
 \int_{-\infty}^{x_0}\Prob(\widehat{\textbf{p}}_x) dx = \Lambda,
 \end{equation}
 where $\Lambda$ is the appropriate number for $2\sigma$. That tells us what $x$ would be needed for us to thing that it was an outlier result without there being an extra $e$ in the data. Then we ask how often we get such an outlier result by computing
  \begin{equation}
 \int_{x_0}^\infty \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) dx.
\end{equation}
Is what you've written equivalent to this? Sorry if this is remedial...
 }
 \begin{equation}
\Prob(P_{e})  =  1 -  \int \Prob(\widehat{\textbf{p}}_x) \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) x
 \end{equation}
 where $\Prob(\widehat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{p}}_{e+x}|P_{e})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{p}}_{x+e}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.

>>>>

In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{\rm out} = \widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$. Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?". \acl{Can we justify better why this is the right question? In particular, why is the detection of an injected signal the right thing to look at? After all, the universe doesn't do any signal injections. I think to justify that signal injections are the right thing to consider in the first place, one requires some sort of correspondence between equations analogous to Equation \eqref{eq:Deriv1} and \eqref{eq:Deriv2}.} Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
\caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
given injection level P$_{\rm in}$. The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal. It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}). We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution. At low injection, $\widehat{\textbf{p}}_{r}$ converges to the data level.
}
\label{fig:Pr_vs_Pin}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
\caption{The probability that an injected signal of level P$_{\rm inj}$
is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{p}}_{x}$ (data).
The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.
\label{fig:Prob_vs_Pin}}
\end{figure}

@@

Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of ``data + 
injected eor" ($\widehat{p}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{p}_x$. 
In other words, what is $e$ such that,
\begin{equation}
\widehat{\textbf{p}}_{e+x} > \widehat{\textbf{p}}_{x},
\end{equation}  
?''  Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance. One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e. the null test) the same.  
 \acl{I'm confused a little by this equation. I would've thought that the right thing to do would be to first compute $x_0$, given implicitly by
 \begin{equation}
 \int_{-\infty}^{x_0}\Prob(\widehat{\textbf{p}}_x) dx = \Lambda,
 \end{equation}
 where $\Lambda$ is the appropriate number for $2\sigma$. That tells us what $x$ would be needed for us to thing that it was an outlier result without there being an extra $e$ in the data. Then we ask how often we get such an outlier result by computing
  \begin{equation}
 \int_{x_0}^\infty \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) dx.
\end{equation}
Is what you've written equivalent to this? Sorry if this is remedial...
 }
 \begin{equation}
\Prob(P_{e})  =  1 -  \int \Prob(\widehat{\textbf{p}}_x) \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) x
 \end{equation}
 where $\Prob(\widehat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{p}}_{e+x}|P_{e})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{p}}_{x+e}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
